---
title: "Extracting data from PostgreSQL soduco DB"
author: "Julie Gravier"
date: "2022-10-27"
output:
  html_document:
    df_print: paged
---

### Packages
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(dbplyr)
library(DBI)
library(RPostgreSQL)
```

### Connection to Postgre DB
```{r}
# unsee pswd
source(file = "password.R")
```

Connexions
```{r}
dsn_name <- "soduco"
dsn_hostname <- "geohistoricaldata.org"
dsn_port <- "5432"
dsn_uid <- "postgres"

tryCatch({
  drv <- dbDriver(drvName = "PostgreSQL")
  print("Connecting to Database…")
  connec <- dbConnect(drv, 
                      dbname = dsn_name,
                      host = dsn_hostname, 
                      port = dsn_port,
                      user = dsn_uid, 
                      password = dsn_pswd)
  print("Database Connected!")
},
error=function(cond) {
  print("Unable to connect to Database.")
})
```

### Connection to useful tables
```{r, warning=FALSE}
# elements = what contain boxes?
elements <- tbl(connec, in_schema("directories", "elements"))
head(elements)

# geocoding = made with geocodeur & gazeteers
geocoding <- tbl(connec, in_schema("directories", "geocoding"))
head(geocoding)
```

### Data on list types and books
Known from Pascal's work (in progress) on github/soduco
```{r}
listetype <- read.csv(file = "directories_adress_lists_index_20220201.csv", 
                        stringsAsFactors = FALSE, encoding = "UTF-8") %>%
  as_tibble()
```

### Tables elements as entries with geocoding
This left_join is enough because all possible geolocations are created as rows and preserved even if empty in the DB.
```{r}
activity_geocoded <- geocoding %>%
  left_join(x = ., y = elements %>%
              filter(type == "ENTRY"),
            by = c("entry_id" = "index")) %>%
  filter(directory %in% c(
    "Lamy_1839", "Didot_1845a", "Didot_1845b", "Didot_1855a", "DidotBottin_1864a", "DidotBottin_1875",
    "DidotBottin_1885a", "DidotBottin_1893a", "DidotBottin_1904a"
  )
  )

show_query(activity_geocoded)
head(activity_geocoded)
count(activity_geocoded)
```


### Selecting name lists only
```{r}
activity_geocoded_listn <- activity_geocoded %>%
  collect() %>%
  left_join(x = ., y = listetype %>%
              select(Code_fichier, liste_type, npage_pdf_d, npage_pdf_f), 
            by = c("directory" = "Code_fichier")) %>%
  mutate(sup_debut = if_else(
    condition = view >= npage_pdf_d,
    true = "dans liste",
    false = "hors liste"
  )) %>%
  mutate(inf_fin = if_else(
    condition = view <= npage_pdf_f,
    true = "dans liste",
    false = "hors liste"
  )) %>%
  mutate(dans_liste = if_else(
    sup_debut == "dans liste" & inf_fin == "dans liste",
    "dans liste", "hors liste"
  )) %>%
  filter(dans_liste == "dans liste") %>%
  select(-sup_debut:-dans_liste) %>%
  filter(liste_type == "ListNoms") %>%
  # the version of the data
  mutate(version = "v2:2022-06-20")

nrow(activity_geocoded_listn)
```

### Output in .xlsx format
```{r}
openxlsx::write.xlsx(x = activity_geocoded_listn, file = "geocoded_entries.xlsx", overwrite = TRUE)
```


```{r}
dbDisconnect(conn = connec)
```
